\wl{CFL Pumping} If $L$ is context-free then there exists a $p \in \mathbb{N}$ such that if $w \in L$ with $|w| \ge p$  then $w$ may be split into \textbf{five} pieces $w = uvxyz$ such that: (1) $uv^ixy^iz \in L \ \forall\ i \in \mathbb{N}$; (2) $|vy| > 0$; and (3) $|vxy| \le p$. Tip: Pick a string $w$ that allows as few cases for partitions of $w = uvxyz$ as possible.
\wde{Chomsky Hierarchy} A grammar $G = (N, \Sigma, P, S)$ is of type: \textbf{0} (or \emph{computably enumerable}) in the general case. \textbf{1} (or \emph{context-sensitive}) if $| \alpha| \le |\beta|$ for all productions $\alpha \to \beta$, except we also allow $S \to \epsilon$ if $S$ does not occur on the RHS of any rule. \textbf{2} (or \emph{context-free}) if all productions are of the form $A \to \alpha$. \textbf{3} (or \emph{right-linear}) if all productions are of the form $A \to w$ or $A \to wB$ where $w \in \Sigma$ and $B \in N$.
\wa{Emptiness of FA} Given a finite automaton, do a depth first search, if you reach a final state not empty, otherwise empty.
\wa{Emptiness of CFLs} Given a CFG for our language: (1) Mark the terminals and $\epsilon$ as generating. (2) Mark as generating all non-terminals which have a production with only generating symbols in their RHS. (3) Repeat until nothing new is marked generating. (4) Check whether $S$ is marked generating.
\wa{Equiv. of Reg Langs} Given two DFAs for $L_1$ and $L_2$, produce a DFA of the symmetric set difference: $(L_1 \cap \overline{L_2}) \cup (L_2 \cap \overline{L_1})$. If this DFA is empty, then the two languages are equal.
\subsection*{Computability}
\wde{RM} A register machine, or RM, consists of: A \textbf{fixed} number $m$ pf registers $R_0 \ldots R_{m-1}$ which each hold a natural number; A \textbf{fixed} program $P$ which is a sequence of $n$ instructions $l_0 \ldots l_{n-1}$. Each instruction is either $\Inc(i)$, which increments register $R_i$, or $\Decjz(i,j)$ which decrements $R_i$ unless $R_i = 0$ in which case it jumps to $I_j$.
\wde{Pairing Functions} A pairing function is an injective function $\mathbb{N} \times \bb{N} \to \bb{N}$. Use $\pair{a,b}$ to denote a pairing function.
\wt{Generalising} A 2-tuple pairing function is enough to cram an arbitrary sequence of natural numbers into one $\mathbb{N}^* \to \mathbb{N}$.